First Order Alternation

### 2018-11-16 quantifiers/body.tex
201811161615
201811161905
ok

\section{Experimental Results}

We have implemented a version of the IMPACT semi-algorithm
\cite{McMillan06} in a prototype tool called FOADA, which is avaliable
online \cite{foada}. The tool is written in Java and uses the Z3 SMT
solver \cite{z3}, via the JavaSMT interface \cite{javasmt}, for
spuriousness and coverage queries and also for interpolant generation.

The experimental results, reported in Table \ref{tab:experiments},
come from several sources, namely predicate automata models (*.pa)
\cite{Farzan15,Farzan16} available online \cite{pa}, timed automata
inclusion problems (abp.ada, train.ada, rr-crossing.foada), array
logic entailments (array\_rotation.ada, array\_simple.ada,
array\_shift.ada) and hardware circuit verification (hw1.ada,
hw2.ada), initially considered in \cite{IosifRV16}. The main advantage
of using FOADA over the INCLUDER \cite{includer} tool used in
\cite{IosifRV16} is the possibility of checking inclusion between
infinite alphabet automata with hidden (local) variables, whose values
are not visible in the input. In particular, this is essential for
checking inclusion of timed automata that use internal clocks to
control the computation.

\begin{table}[htb]
\vspace*{-\baselineskip}
\begin{center}
{\fontsize{7}{8}\selectfont
\begin{tabular}{||l|c|c|c|c|c||}
\hline
Example & $\len{\A}$ (bytes) & $L(\A)=\emptyset$ ? & Nodes Expanded & Nodes Visited & Times (ms) \\
\hline
incdec.pa & 499 & no & 13 & 7 & 273 \\
\hline
localdec.pa & 678 & no & 17 & 11 & 560 \\
\hline
ticket.pa & 4250 & no & 31 & 17 & 999 \\
\hline
count\_thread0.pa & 9767 & no & 100 & 76 & 6055 \\
\hline
count\_thread1.pa & 10925 & no & 766 & 692 & 74445 \\
\hline
array\_rotation.ada & 1834 & yes & 9 & 8 & 1543 \\
\hline
array\_simple.ada & 3440 & yes & 11 & 10 & 6787 \\
\hline
array\_shift.ada & 874 & yes & 6 & 5 & 413 \\
\hline
abp.ada & 6909 & no & 52 & 47 & 4788 \\
\hline
train.ada & 1823 & yes & 68 & 67 & 7319 \\
\hline
hw1.ada & 322 & Solver Error & / & / & / \\
\hline
hw2.ada & 674 & yes & 20 & 22 & 4974 \\
\hline
rr-crossing.foada & 1780 & yes & 67 & 67 & 7574 \\
\hline
\end{tabular}
}
\caption{Experiments with First Order Alternating Automata}
\label{tab:experiments}
\end{center}
\vspace*{-2\baselineskip}
\end{table}

The experiments were carried out on a MacOS x64 - 1.3 GHz
  Intel Core i5 - 8 GB 1867 MHz LPDDR3 machine.

>>>>

\vspace*{-0.5\baselineskip}
\section{Experimental Results}
\vspace*{-0.5\baselineskip}

We have implemented a version of the IMPACT semi-algorithm
\cite{McMillan06} in a prototype tool called FOADA, which is avaliable
online \cite{foada}. The tool is written in Java and uses the Z3 SMT
solver \cite{z3}, via the JavaSMT interface \cite{javasmt}, for
spuriousness and coverage queries and also for interpolant generation.
The experiments were carried out on a MacOS x64 - 1.3 GHz Intel Core
i5 - 8 GB 1867 MHz LPDDR3 machine.

The experimental results, reported in Table \ref{tab:experiments},
come from several sources, namely predicate automata models (*.pa)
\cite{Farzan15,Farzan16} available online \cite{pa}, timed automata
inclusion problems ({\tt abp.ada}, {\tt train.ada}, {\tt
  rr-crossing.foada}), array logic entailments ({\tt
  array\_rotation.ada}, {\tt array\_simple.ada}, {\tt
  array\_shift.ada}) and hardware circuit verification ({\tt hw1.ada},
{\tt hw2.ada}), initially considered in \cite{IosifRV16}. The {\tt
  train-simpleN.} {\tt foada} and {\tt fischer-mutexN.foada} examples are
parametric verification problems in which one checks inclusions of the
form $\bigcap_{i=1}^N\lang{A_i} \subseteq \lang{B}$, where $A_i$ is
the $i$-th copy of the same template automaton.

The advantage of using FOADA over the INCLUDER \cite{includer} tool
from \cite{IosifRV16} is the possibility of having infinite alphabet
automata with hidden (local) variables, whose values are not visible
in the input. In particular, this is essential for checking inclusion
of timed automata that use internal clocks to control the computation.

\begin{table}[htb]
\vspace*{-\baselineskip}
\begin{center}
{\fontsize{7}{8}\selectfont
\begin{tabular}{||l|c|c|c|c|c||}
\hline
Example & $\len{\A}$ (bytes) & $L(\A)=\emptyset$ ? & Nodes Expanded & Nodes Visited & Time (ms) \\
\hline
incdec.pa & 499 & no & 21 & 17 & 779 \\
\hline
localdec.pa & 678 & no & 49 & 35 & 1814 \\
\hline
ticket.pa & 4250 & no & 229 & 91 & 9543 \\
\hline
count\_thread0.pa & 9767 & no & 154 & 128 & 8553 \\
\hline
count\_thread1.pa & 10925 & no & 766 & 692 & 76771 \\
\hline
local0.pa & 10595 & no & 73 & 27 & 1431 \\
\hline
local1.pa & 11385 & no & 1135 & 858 & 101042 \\
\hline
array\_rotation.ada & 1834 & yes & 9 & 8 & 1543 \\
\hline
array\_simple.ada & 3440 & yes & 11 & 10 & 6787 \\
\hline
array\_shift.ada & 874 & yes & 6 & 5 & 413 \\
\hline
abp.ada & 6909 & no & 52 & 47 & 4788 \\
\hline
train.ada & 1823 & yes & 68 & 67 & 7319 \\
\hline
hw1.ada & 322 & Solver Error & / & / & / \\
\hline
hw2.ada & 674 & yes & 20 & 22 & 4974 \\
\hline
rr-crossing.foada & 1780 & yes & 67 & 67 & 7574 \\
% \hline
% running2.foada & 1217 & yes & 13 & 13 & 788 \\
\hline
train-simple1.foada & 5421 & yes & 43 & 44 & 2893 \\
\hline
train-simple2.foada & 10177 & yes & 111 & 113 & 8386 \\
\hline
train-simple3.foada & 15961 & yes & 196 & 200 & 15041 \\
% \hline
% fischer-mutex1.foada & 1566 & no & 31 & 31 & 1552 \\
\hline
fischer-mutex2.foada & 3000 & yes & 23 & 23 & 808 \\
\hline
fischer-mutex3.foada & 4452 & yes & 33 & 33 & 1154 \\
\hline
\end{tabular}
}
\caption{Experiments with First Order Alternating Automata}
\label{tab:experiments}
\end{center}
\vspace*{-2\baselineskip}
\end{table}
